Claret: Using Data Types for Highly Concurrent Distributed Transactions

### 2015-09-23 papoc/paper.Rmd
fix acm number
fix broken ref to bloom -> bloomfilter

conference:
  name: PaPoC'15
  location: 'April 21, 2015, Bordeaux, France'
  year: 2015
  copyrightdata: 978-1-4503-3238-5/15/04

@@

**Probabilistic data types** such as *bloom filters* [@bloom], *hyperloglogs* [@hyperloglog], and *count-min sketches* [@countminsketch] trade off accuracy (within fixed bounds) for better performance or storage. Twitter's streaming analytics system [@summingbird] and many machine learning algorithms leverage these to handle high data volume, and we expect similar benefit.

>>>>

conference:
  name: PaPoC'15
  location: 'April 21, 2015, Bordeaux, France'
  year: 2015
  copyrightdata: 978-1-4503-3537-9/15/04

@@

**Probabilistic data types** such as *bloom filters* [@bloomfilter], *hyperloglogs* [@hyperloglog], and *count-min sketches* [@countminsketch] trade off accuracy (within fixed bounds) for better performance or storage. Twitter's streaming analytics system [@summingbird] and many machine learning algorithms leverage these to handle high data volume, and we expect similar benefit.
